\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{geometry}
\fancyhf{}

\geometry{top=0.5in}
\pagestyle{plain}

\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Aditya}{Shukla}{Software engineer skilled in crafting web solutions with proficiency in frontend and backend technologies.}{\contactline{\href{mailto:shukladitya9@gmail.com}{shukladitya9@gmail.com}}
{\href{tel:+918130712435}{(+91) 8130712435}}
{\href{https://shukladitya.github.io/}{shukladitya.github.io}}
{\href{https://github.com/shukladitya}{github.com/shukladitya}}{\href{https://www.linkedin.com/in/adityashk/}{linkedin.com/in/adityashk}}{\href{https://leetcode.com/shukladitya9/}{leetcode.com/shukladitya9}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\workexperience{Software Development Engineer}{{\href{https://klubworks.com/}{Klub}}}{June 2023}{Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\sectiontopsep
\item Worked on the internal tool 'Portal' to create disbursal and risk workflows, integrating with Zeebe orchestration engine to streamline business process automation.
\item Developed API endpoints for key features such as DRR funnel and Camunda like clone \mbox{'Operate'} for monitoring and visualizing the state of active workflows. 
\item Managed legacy services 'taskr' and 'utility,' authored test cases achieving over 95\% code coverage.
\item Developed, integrated Slack Bots to enhance task distribution and monitoring.
\end{tightemize}
\sectionbottomsep


\workexperience{Web Developer Intern}{{\href{https://unacademy.com/}{Unacademy}}}{March 2023}{May 2023}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Part of NextLevel team, an AI based job searching platform, working on companies’ \mbox{section} (Recruiter flow) using NextJS.
\item Contributed to the initial web setup and development of a core component library, while establishing app-wide state management architecture using Zustand.
\end{tightemize}
\sectionbottomsep


\workexperience{Frontend Developer Intern}{{\href{https://skylarkdrones.com/}{Skylark Drones}}}{January 2023}{March 2023}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Contributed to the Spectra team, specializing in geo-spatial data processing and \mbox{visualization}, instrumental in the development of Spectra 2.0, and led the migration from the legacy application.

\item Created map-based Vue.js components utilizing Mapbox GL, pinia for efficient \mbox{geo-spatial} data visualization within the application.

\end{tightemize}
\sectionbottomsep


\workexperience{SDE Intern}{{\href{https://tagmango.com/}{TagMango (YC W20)}}}{July 2022}{December 2022}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Consistently developed and debugged new features for a rapidly growing SaaS \mbox{platform}. \mbox{Implemented} optimizations such as app-wide code splitting, transitioning from context to Redux, and PropTypes compliance. 
\item Developed standalone applications, including a component library with storybook,\mbox{ Progressive Web App}, and Takedown-CRM for takedown requests. 

\end{tightemize}
\sectionbottomsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\projectheading{{\href{https://www.mypennyprofit.com/}{PennyProfit (Freelance)}}}{| Flutter, dart}
\begin{tightemize}
\item Built, documented, deployed mobile application that will run on android and iOS \mbox{platforms}, taking existing web-app as the blueprint.
\end{tightemize}
\sectionbottomsep

\projectheading{{\href{https://github.com/shukladitya/1v1-multiplayer}{1VS1 Multiplayer}}}{| Canvas, Socket.io, Express, Firebase}
\begin{tightemize}
\item Pixel art-style fighting game with cross-platform functionality, playable in both online and offline modes.
\end{tightemize}
\sectionbottomsep

\projectheading{{\href{https://github.com/shukladitya/meishi}{Meishi}}}{| React, Firebase(Auth), MongoDB, Express, Node.js}
\begin{tightemize}
\item A platform for creating, sharing and storing digital business cards. 
\end{tightemize}
\sectionbottomsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2020	     & Finalist & Lorem Ipsum\\
% 2018	     & $2^{nd}$ & Dolor Sit Amet\\
% 2015	     & Finalist  & Cras posuere\\
% \\
% \end{tabular}
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\skillcat{Programming Languages}\\[3pt]
JavaScript, Typescript, C++, Dart, SCSS, Python, \LaTeX\
\sectionbottomsep

\skillcat{Libraries \& Frameworks}\\[3pt]
Next.js, NestJS, React,Node.js, Flutter, Vue.js, Socket.io, Express
\sectionbottomsep

\skillcat{Tools \& Platforms}\\[3pt]
Git, Github, GraphQL, Netlify, Vercel, Docker, Firebase, \mbox{Storybook}, Figma
\sectionbottomsep


% \sectionbottomsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\skillcat{Bachelor of \mbox{engineering}}\\[3pt]
J.S.S Academy of Technical Education, Bengaluru\\
August 2019-June 2023
\begin{tightemize}
\item 8.8 CGPA 
\end{tightemize}
\sectionbottomsep

\skillcat{Secondary School}\\[3pt]
Army Public School\\
May 2016-May 2018
\begin{tightemize}
\item HSC - 89.6%
\item SSC - 10 CGPA
\end{tightemize}


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     Responsibilities
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Responsibilities} 
\skillcat{JSS Developers Group}\\[3pt]
Tech Lead\\
\skillcat{Codechef College Chapter}
Outreach and Media Lead



% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     Achievements
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements} 
\achievementitem{Winner,}{SAMYOG Project \mbox{Presentation} (July 2022)}\\[5pt]
\achievementitem{Third,}{Honeywell Hackwell 3.0 (April 2022)}\\[5pt]
\achievementitem{Finalist,}{Honeywell Hackwell 2.0 (June 2021) }

\end{minipage} 
 \end{document}  \documentclass[]{article}

